Versioned data: why it is needed and how it can be achieved (easily and cheaply)

### 2017-09-21 ms.tex
an alternative abstract to address #21

>>>>

% Alternative abstract, to introduce versioning problem earlier, leaving the small versus large issue until later

The sharing and re-use of data has become a cornerstone of modern science.  To help this process, numerous linked tools have been developed to allow quick and easy data sharing:    a data file for a particular analysis can be quickly uploaded, given a digital identifier, and shared.  Thus far, however, this framework does not account for on-going scientific progress: for many important problems, epitomised by problems that lead to one or more meta-analyses, datasets will continue to grow with time---more data points will be added, and new and more useful data structures will be created.  Essentially this means that datasets, like science in general, progress with time.  We suggest that many different datasets would be more useful if organized as a series of versions, with a simple naming system to allow users to perceive the type of change between versions.  In this article, we argue that adopting the paradigm and processes for versioned data, analogous to software versioning, would be useful for both data curators and users of even small-to-medium sized datasets. We introduce a system called Versioned Data Delivery (VDD) and present tools for creating, archiving, and distributing versioned data easily, quickly, and cheaply. These new tools allow for individual research groups to shift from a static model of data curation to a dynamic and versioned model that naturally matches the scientific process.
